### 2014-06-23 tex/main-body-text.tex
edited description of flock

\citet{Duc&Tur2012} promote a method for using {\sc flock} to estimate, $K$, the number of
subpopulations. The user must first specify the number of runs (different initial allocation of individuals 
to each cluster) as well as the number of iterations individual has the chance to be reallocated 
to a different cluster. For each run the log-likelihood value of membership to all $K$ clusters is computed
and the difference between the cluster with the highest likelihood and second highest likelihood is reported (LLOD)
for each individual. Runs that converge on the same solution are indicated by the same mean LLOD score. and 
are referred to as a plateau. If for a given $k$ there may be multiple local maxima in addition to 
the global maximum, depending on the initial allocation of individuals the alorithm will result in finding
different plateaus. The plateau record is a list of how many runs ended up at these different solutions. 
\citet{Duc&Tur2012} developed two stopping rules that lead to the estimation of $K$. In the abscence of 
reasonable values for $k$ \citet{Duc&Tur2012} advocate running  {\sc flock} until either a single plateau 
$\geq 6$  is reached or four consecutive $k$ values yield no plateaus. If the first stopping condition is satisfied,
the $K$ for which there is a a single plateau $\geq 6$ is the point estimate for $K$. Alternatively, 
if multiple plateaus are observed with at least one plateau $\geq 6$, the largest value of $K$ that satisfies 
this conditon should be taken as the lower bound estimate of $K$. If no plateaus $\geq 6$ are observed $K$
is \textit{undecided}.

@@

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space for any given k can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind. The results of {\sc flock} depend primarily on the initial partition of 
individuals. It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as \textit{k} increases
{\sc flock} finds suboptimal allocations.

>>>>

\citet{Duc&Tur2012} promote a method for using {\sc flock} to estimate, $K$, the number of
subpopulations. The user must first specify the number of runs (different initial allocation of individuals 
to each cluster) as well as the number of iterations each individual has the opportunity to be reallocated 
to a different cluster. For each run, the log-likelihood value of membership to all $K$ clusters is computed
and the log likelihood difference (LLOD), the difference between the cluster with the highest likelihood 
and second highest likelihood, is reported for each individual. Runs that converge on the same solution 
are indicated by the same mean LLOD score and 
are referred to as a plateau. The plateau record is a list of how many runs ended up at these different solutions. 
\citet{Duc&Tur2012} developed two stopping rules that lead to the estimation of $K$. In the abscence of 
reasonable values for $k$ \citet{Duc&Tur2012} advocate running  {\sc flock} until either a single plateau 
$\geq 6$  is reached or four consecutive $k$ values yield no plateaus. If the first stopping condition is satisfied,
the $K$ for which there is a a single plateau $\geq 6$ is the point estimate for $K$. Alternatively, 
if multiple plateaus are observed with at least one plateau $\geq 6$, the largest value of $K$ that satisfies 
this conditon should be taken as the lower bound estimate of $K$. If no plateaus $\geq 6$ are observed $K$
is \textit{undecided}.

@@

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space for any given k can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind. The likelihood surface may be characterized by multiple peaks and troughs.
The peak or plateau that the  {\sc flock} algorithm finds is entirely dependent on the initial allocation of 
individuals. It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as \textit{k} increases
{\sc flock} finds suboptimal allocations.
